Performances Code

### 2019-02-01 Scripts/performances.rmd
editted script of results

@@

#Barplots of performance metrics

@@

##Accuracy

>>>>

gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

gm12878_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
gm12878_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
gm12878_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

K562_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
K562_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
K562_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
K562_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
K562_10kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

K562_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
K562_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
K562_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
K562_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
K562_25kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

K562_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
K562_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
K562_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
K562_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
K562_50kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

K562_100kb_none_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/RFE/prcurve.rds")$auc.integral
K562_100kb_rus_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/RFE/prcurve.rds")$auc.integral
K562_100kb_ros_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/RFE/prcurve.rds")$auc.integral
K562_100kb_smote_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/RFE/prcurve.rds")$auc.integral
K562_100kb_rose_oc <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OC/RFE/prcurve.rds")$auc.integral

gm12878_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
gm12878_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
gm12878_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

gm12878_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
gm12878_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
gm12878_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

gm12878_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
gm12878_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
gm12878_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

gm12878_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
gm12878_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
gm12878_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

K562_10kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
K562_10kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
K562_10kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
K562_10kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
K562_10kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

K562_25kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
K562_25kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
K562_25kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
K562_25kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
K562_25kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

K562_50kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
K562_50kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
K562_50kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
K562_50kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
K562_50kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

K562_100kb_none_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/RFE/prcurve.rds")$auc.integral
K562_100kb_rus_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/RFE/prcurve.rds")$auc.integral
K562_100kb_ros_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/RFE/prcurve.rds")$auc.integral
K562_100kb_smote_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/RFE/prcurve.rds")$auc.integral
K562_100kb_rose_OP <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/OP/RFE/prcurve.rds")$auc.integral

gm12878_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

gm12878_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

gm12878_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

gm12878_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
gm12878_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

K562_10kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
K562_10kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
K562_10kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
K562_10kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
K562_10kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

K562_25kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
K562_25kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
K562_25kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
K562_25kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
K562_25kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

K562_50kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
K562_50kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
K562_50kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
K562_50kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
K562_50kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

K562_100kb_none_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/prcurve.rds")$auc.integral
K562_100kb_rus_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/prcurve.rds")$auc.integral
K562_100kb_ros_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/prcurve.rds")$auc.integral
K562_100kb_smote_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/prcurve.rds")$auc.integral
K562_100kb_rose_Distance <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/prcurve.rds")$auc.integral

gm12878_10kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
gm12878_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
gm12878_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
gm12878_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

gm12878_25kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
gm12878_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
gm12878_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
gm12878_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

gm12878_50kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
gm12878_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
gm12878_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
gm12878_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

gm12878_100kb_none_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
gm12878_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
gm12878_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
gm12878_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

K562_10kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
K562_10kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
K562_10kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
K562_10kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
K562_10kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

K562_25kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
K562_25kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
K562_25kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
K562_25kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
K562_25kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

K562_50kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
K562_50kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
K562_50kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
K562_50kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
K562_50kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

K562_100kb_none_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/all/RFE/prcurve.rds")$auc.integral
K562_100kb_rus_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/all/RFE/prcurve.rds")$auc.integral
K562_100kb_ros_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/all/RFE/prcurve.rds")$auc.integral
K562_100kb_smote_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/all/RFE/prcurve.rds")$auc.integral
K562_100kb_rose_all <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/all/RFE/prcurve.rds")$auc.integral

prcurvetable <- data.frame(CL=c(rep("GM12878", 20), rep("K562", 20)),
                           Resolution=c(c(rep("10 kb", 5), 
                                        rep("25 kb", 5),
                                        rep("50 kb", 5),
                                        rep("100 kb", 5)),
                                        c(rep("10 kb", 5), 
                                        rep("25 kb", 5),
                                        rep("50 kb", 5),
                                        rep("100 kb", 5))),
                           ReSampling=rep(c("None",
                                        "RUS",
                                        "ROS",
                                        "SMOTE",
                                        "ROSE"),8))
prcurvetable$OC <- c(gm12878_10kb_none_oc,
gm12878_10kb_rus_oc,
gm12878_10kb_ros_oc,
gm12878_10kb_smote_oc,
gm12878_10kb_rose_oc,
gm12878_25kb_none_oc,
gm12878_25kb_rus_oc,
gm12878_25kb_ros_oc,
gm12878_25kb_smote_oc,
gm12878_25kb_rose_oc,
gm12878_50kb_none_oc,
gm12878_50kb_rus_oc,
gm12878_50kb_ros_oc,
gm12878_50kb_smote_oc,
gm12878_50kb_rose_oc,
gm12878_100kb_none_oc,
gm12878_100kb_rus_oc,
gm12878_100kb_ros_oc,
gm12878_100kb_smote_oc,
gm12878_100kb_rose_oc,
K562_10kb_none_oc,
K562_10kb_rus_oc,
K562_10kb_ros_oc,
K562_10kb_smote_oc,
K562_10kb_rose_oc,
K562_25kb_none_oc,
K562_25kb_rus_oc,
K562_25kb_ros_oc,
K562_25kb_smote_oc,
K562_25kb_rose_oc,
K562_50kb_none_oc,
K562_50kb_rus_oc,
K562_50kb_ros_oc,
K562_50kb_smote_oc,
K562_50kb_rose_oc,
K562_100kb_none_oc,
K562_100kb_rus_oc,
K562_100kb_ros_oc,
K562_100kb_smote_oc,
K562_100kb_rose_oc)

prcurvetable$OP <- c(gm12878_10kb_none_OP,
gm12878_10kb_rus_OP,
gm12878_10kb_ros_OP,
gm12878_10kb_smote_OP,
gm12878_10kb_rose_OP,
gm12878_25kb_none_OP,
gm12878_25kb_rus_OP,
gm12878_25kb_ros_OP,
gm12878_25kb_smote_OP,
gm12878_25kb_rose_OP,
gm12878_50kb_none_OP,
gm12878_50kb_rus_OP,
gm12878_50kb_ros_OP,
gm12878_50kb_smote_OP,
gm12878_50kb_rose_OP,
gm12878_100kb_none_OP,
gm12878_100kb_rus_OP,
gm12878_100kb_ros_OP,
gm12878_100kb_smote_OP,
gm12878_100kb_rose_OP,
K562_10kb_none_OP,
K562_10kb_rus_OP,
K562_10kb_ros_OP,
K562_10kb_smote_OP,
K562_10kb_rose_OP,
K562_25kb_none_OP,
K562_25kb_rus_OP,
K562_25kb_ros_OP,
K562_25kb_smote_OP,
K562_25kb_rose_OP,
K562_50kb_none_OP,
K562_50kb_rus_OP,
K562_50kb_ros_OP,
K562_50kb_smote_OP,
K562_50kb_rose_OP,
K562_100kb_none_OP,
K562_100kb_rus_OP,
K562_100kb_ros_OP,
K562_100kb_smote_OP,
K562_100kb_rose_OP)

prcurvetable$Distance <- c(gm12878_10kb_none_Distance,
gm12878_10kb_rus_Distance,
gm12878_10kb_ros_Distance,
gm12878_10kb_smote_Distance,
gm12878_10kb_rose_Distance,
gm12878_25kb_none_Distance,
gm12878_25kb_rus_Distance,
gm12878_25kb_ros_Distance,
gm12878_25kb_smote_Distance,
gm12878_25kb_rose_Distance,
gm12878_50kb_none_Distance,
gm12878_50kb_rus_Distance,
gm12878_50kb_ros_Distance,
gm12878_50kb_smote_Distance,
gm12878_50kb_rose_Distance,
gm12878_100kb_none_Distance,
gm12878_100kb_rus_Distance,
gm12878_100kb_ros_Distance,
gm12878_100kb_smote_Distance,
gm12878_100kb_rose_Distance,
K562_10kb_none_Distance,
K562_10kb_rus_Distance,
K562_10kb_ros_Distance,
K562_10kb_smote_Distance,
K562_10kb_rose_Distance,
K562_25kb_none_Distance,
K562_25kb_rus_Distance,
K562_25kb_ros_Distance,
K562_25kb_smote_Distance,
K562_25kb_rose_Distance,
K562_50kb_none_Distance,
K562_50kb_rus_Distance,
K562_50kb_ros_Distance,
K562_50kb_smote_Distance,
K562_50kb_rose_Distance,
K562_100kb_none_Distance,
K562_100kb_rus_Distance,
K562_100kb_ros_Distance,
K562_100kb_smote_Distance,
K562_100kb_rose_Distance)

prcurvetable$All <- c(gm12878_10kb_none_all,
gm12878_10kb_rus_all,
gm12878_10kb_ros_all,
gm12878_10kb_smote_all,
gm12878_10kb_rose_all,
gm12878_25kb_none_all,
gm12878_25kb_rus_all,
gm12878_25kb_ros_all,
gm12878_25kb_smote_all,
gm12878_25kb_rose_all,
gm12878_50kb_none_all,
gm12878_50kb_rus_all,
gm12878_50kb_ros_all,
gm12878_50kb_smote_all,
gm12878_50kb_rose_all,
gm12878_100kb_none_all,
gm12878_100kb_rus_all,
gm12878_100kb_ros_all,
gm12878_100kb_smote_all,
gm12878_100kb_rose_all,
K562_10kb_none_all,
K562_10kb_rus_all,
K562_10kb_ros_all,
K562_10kb_smote_all,
K562_10kb_rose_all,
K562_25kb_none_all,
K562_25kb_rus_all,
K562_25kb_ros_all,
K562_25kb_smote_all,
K562_25kb_rose_all,
K562_50kb_none_all,
K562_50kb_rus_all,
K562_50kb_ros_all,
K562_50kb_smote_all,
K562_50kb_rose_all,
K562_100kb_none_all,
K562_100kb_rus_all,
K562_100kb_ros_all,
K562_100kb_smote_all,
K562_100kb_rose_all)

@@

#Barplots of performance metrics for models with distance-type predictors

@@

##None
rfperf_gm12878_10kb_none <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/RF/rfperf.rds")

##ROSE
rfperf_gm12878_10kb_rose <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/RF/rfperf.rds")

#K562

##None
rfperf_K562_10kb_none <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/RF/rfperf.rds")
